Verifying Demonstrations

### 2020-03-13 paper/DB-Schnorr-PKI.tex
Changes some equations to display, fixes bugs in eqns
Fixes some equations that breaks boxes

In summary, the difference is as follows.
\(\DBS\) performs \(
  \PK[\alpha][A = g^\alpha]
\) with a distance bound on the user's behalf.
\(\DBSHW\) first runs \iac{DHKE} to establish a shared key~\(k =
\gDH^{\xDH \yDH}\) from \(\XDH = \gDH^{\xDH}, \YDH = \gDH^{\yDH}\), then 
performs \[
  \PK[\alpha, \xDH, \sk_P, \sigma][
    A = g^\alpha \land
    \XDH = \gDH^{\xDH} \land
    \XDHCL = \XDH^{\sk} \land
    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
  ],
\] also with a distance bound and \(A = g^\alpha\) on behalf of the user; where 
\(\sk_P\) is the prover's private key, \(\sigma\) is a signature issued with 
signing key~\(\sk\) and \(\Blind\) reblinds a signature.
Proving knowledge of \(\XDH = \gDH^{\xDH}\) and \(\XDHCL = \XDH^{\sk}\) 
prevents any \ac{MITM} attack against the \ac{DHKE}.
Proving knowledge of a signature~\(\sigma\) by \iac{CA} on the private 
key~\(\sk_P\) ensures that the prover is a device in the \ac{PKI} of the 
\ac{CA}.

@@

Now the \ac{CA} computes the signature~\(\sigma = (a, A, b, B, c)\), where \[
  \alpha\rgets \ZZ_{\qCL}, \quad a\gets \gCL^\alpha, \quad
  A\gets \gCL^{\zCL}, \quad
  b\gets a^{\yCL}, \quad
  B\gets A^{\yCL}, \quad
  c\gets a^{\xCL} M^{\alpha \xCL \yCL}
\] and gives to the prover.

@@

The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
\dotsc, c_m\rgets \bin^l\), and sends these to the prover.
The prover computes responses
\begin{multline*}
  s_i\gets \rho - c_i\alpha, \quad
  \sDH_i\gets \rhoDH - c_i \xDH, \\%\quad
  \sCL_i^{(r')}\gets \rhoCL_{r'} + c_i r', \quad
  \sCL_i^{(\sk)}\gets \rhoCL_{\sk} - c_i \sk, \quad
  \sCL_i^{(r)}\gets \rhoCL_r - c_i r
\end{multline*}
for \(i\in \{1, \dotsc, m\}\), where \(r' = r_2^{-1}\).

>>>>

In summary, the difference is as follows.
\(\DBS\) performs \(
  \PK[\alpha][A = g^\alpha]
\) with a distance bound on the user's behalf.
\(\DBSHW\) first runs \iac{DHKE} to establish a shared key~\(k =
\gDH^{\xDH \yDH}\) from \(\XDH = \gDH^{\xDH}, \YDH = \gDH^{\yDH}\), then 
performs
\begin{multline*}
  \PK\big\{ (\alpha, \xDH, \sk_P, \sigma) : \\
    A = g^\alpha \land
    \XDH = \gDH^{\xDH} \land
    \XDHCL = \XDH^{\sk} \land \\
    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
  \big\},
\end{multline*}
also with a distance bound and \(A = g^\alpha\) on behalf of the user; where 
\(\sk_P\) is the prover's private key, \(\sigma\) is a signature issued with 
signing key~\(\sk\) and \(\Blind\) reblinds a signature.
Proving knowledge of \(\XDH = \gDH^{\xDH}\) and \(\XDHCL = \XDH^{\sk}\) 
prevents any \ac{MITM} attack against the \ac{DHKE}.
Proving knowledge of a signature~\(\sigma\) by \iac{CA} on the private 
key~\(\sk_P\) ensures that the prover is a device in the \ac{PKI} of the 
\ac{CA}.

@@

Now the \ac{CA} computes the signature~\(\sigma = (a, A, b, B, c)\), where
\begin{multline*}
  \alpha\rgets \ZZ_{\qCL}, \quad a\gets \gCL^\alpha, \quad
  A\gets \gCL^{\zCL}, \quad
  b\gets a^{\yCL}, \\
  B\gets A^{\yCL}, \quad
  c\gets a^{\xCL} M^{\alpha \xCL \yCL}
\end{multline*}
and gives to the prover.

@@

The verifier chooses \(m\) challenges of length \(l\), \[
  c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l,
\] and sends these to the prover.
The prover computes responses
\begin{multline*}
  s_i\gets \rho - c_i\alpha, \quad
  \sDH_i\gets \rhoDH - c_i \xDH, \\%\quad
  \sCL_i^{(r')}\gets \rhoCL_{r'} + c_i r', \quad
  \sCL_i^{(\sk)}\gets \rhoCL_{\sk} - c_i \sk, \quad
  \sCL_i^{(r)}\gets \rhoCL_r - c_i r
\end{multline*}
for \(i\in \{1, \dotsc, m\}\), where \(r' = r_2^{-1}\).
